Forecasting the 2024 Election: Tight Margins and Swing State Uncertainty

### 2024-11-04 paper/paper.qmd
Appendix B update

## Overview
Using a $100K budget, this appendix outlines a carefully designed survey methodology for predicting the 2024 US Presidential Election. The objective is to collect representative, high-quality data using recruiting, poll aggregation, and selective sample methods. Through rigorous validation, this approach ensures data accuracy and reduces common survey research errors.

## Sampling Approach
We will implement stratified random sampling to ensure that key demographic and geographic subgroups are fairly represented. This approach reduces bias and offers more reliable insights into voter preference.

**Stratification Criteria:**  
- Age Groups  
- Gender  
- Education Levels  
- Geographic Representation  
- Political Affiliation

**Sample Size Goal:** 10,000 respondents across states and demographics to achieve **high statistical power** with a margin of error below ±1%

**Trade-offs:**  
- Although stratified sampling increases representativeness, it necessitates accurate demographic information and may raise operating expenses.  
- **Missing Data:** It’s possible that some demographics (e.g. men) may be less likely to respond. Post-stratification weighting and data imputation will be used to address this issue.

## Recruitment Strategy
Outline outreach and telephone surveys will be combined in our recruitment strategy to ensure widespread participation from various demographic groups.

@@

**Random-Digit Dialing (RDD):**  
- Phone outreach to reach older, rural voters with poor internet connection. 
- Budget Allocation: $30,000

**Incentives:**  
- Participants are offered $5 gift cards to increase response rates. 
- Budget Allocation: $20,000

**Non-Response Handling:**  
- Increase recruitment incentives for underrepresented groups and use numerous follow-up reminders.

## Data Validation
To ensure the accuracy and reliability of responses, we will implement several data validation techniques:

**Survey Logic Check:**  
- Recognize and flag responses contradicting one another (e.g., reporting under 18 but registered to vote).  
**Attention Check:**  
- Utilize questions to confirm respondents are actively engaged (e.g., “Select ‘Confirm’ to start questionnaire”)  
**Post-Stratification Weighting: **  
- Adjusting for over- and under-enumeration and weighting the sample to reflect the demographic of the US population.

**Mode and Measurement Errors:**   
- We mitigate the impact of using mixed modes (online and telephones) by training enumerators and reducing enumerator bias. Misreporting will be reduced through straightforward questions.

## Poll Aggregation Methodology
We will employ a poll-of-polls aggregation method to reduce bias and smooth fluctuation across individual polls.

**Weighting Criteria:**  
**Sample Size:** larger samples receive more weight to mirror greater reliability.

@@

## Survey Implementation 
Google Forms was used to create and implement the survey, allowing for efficient data collection and safe storage. The main section and sample questions are listed below.

@@

**Survey Overview** \
**Title:** 2024 US Presidential Election Poll \
**Purpose:** To gather public sentiment and predict election outcomes. \
**Estimated Time:** Less than 5 minutes \
**Confidentiality:** All responses are anonymous and used only for research purposes.

1. What is your age?
- Under 18
- 18-24
- 25-34
- 35-44
- 45-54
- 55-64
- 65+

2. What is your gender?
- Male
- Female
- Non-binary / Prefer not to say

3. What is the highest level of education you have completed?
- Less than high school
- High school diploma or GED
- Some college
- Bachelor’s degree
- Master’s degree or higher

4. Are you registered to vote?
- Yes
- No

5. Who do you intend to vote for in the upcoming presidential election?
- Donald Trump (Republican)
- Kamala Harris (Democrat)
- Other
- Undecided

6. How likely are you to vote in the upcoming election?
- Very Likely
- Somewhat Likely
- Not Likely

@@

## Conclusion
This survey methodology uses stratified sampling, multi-channel recruitment, and rigorous data validation procedures to ensure accurate forecasting of the 2024 US Presidential Election. We provide a more stable and reliable prediction through poll-polls aggregation, smoothing out fluctuations across polls. This design balances accuracy, inclusivity, and efficiency with a carefully considered $100K budget, ensuring the poll gathers meaningful insights into voter sentiment and behavior.

>>>>

## Overview
With a budget of $100K, this appendix outlines the survey methodology designed to predict the 2024 U.S. Presidential Election. The goal is to collect representative, high-quality data using recruiting, poll aggregation, and selective sample methods. This approach aims to minimize errors commonly encountered in survey research and to produce reliable insights.

## Sampling Approach
We will use stratified random sampling to ensure fair representation across key demographic and geographic subgroups. This approach reduces bias and provides a more accurate view of voter preferences.

**Stratification Criteria:**  
- Age Groups  
- Gender  
- Education Levels  
- Geographic Regions  
- Political Affiliation

**Sample Size Goal:**   
- 10,000 respondents across states and demographics to achieve **high statistical power** with a margin of error below ±1%

**Trade-offs:**  
- While stratified sampling improves representativeness, it requires precise demographic data, which can increase costs.

**Missing Data:**  
- Specific demographics (e.g., younger males) may have lower response rates. To address this, we will use **post-stratification weighting** and **data imputation**.

## Recruitment Strategy
To ensure a broad demographic reach, we will combine **online recruitment** and **random-digit dialing (RDD)** for telephone surveys. This approach targets both urban and rural populations, increasing inclusivity.

@@

**Random-Digit Dialing (RDD):**  
- Phone surveys to engage older and rural voters with limited internet access. 
- Budget Allocation: $30,000

**Incentives:**  
- $5 gift cards offered to participants to increase response rates.
- Budget Allocation: $20,000

**Non-Response Handling:**  
- Increase incentives for underrepresented groups and send multiple follow-up reminders.

## Data Validation
To ensure data quality, several validation techniques will be implemented:

**Survey Logic Check:**  
- Identifies and flags contradictory responses (e.g., respondents under 18 claiming voter registration).   
**Attention Check:**  
- Includes questions to confirm active engagement (e.g., “Select ‘Confirm’ to proceed”) 
**Post-Stratification Weighting: **  
- Adjusts the sample for over- and under-enumeration and weighting to reflect the demographic composition of the U.S. population.

**Mode and Measurement Errors:**   
- Enumerators will be trained to reduce inconsistencies between online and phone responses, and survey questions will be straightforward to minimize misreporting.

## Poll Aggregation Methodology
A **poll-of-polls aggregation** method will be applied to reduce bias and balance fluctuation between individual polls.

**Weighting Criteria:**  
**Sample Size:** larger samples receive higher weight for greater reliability.

@@

## Survey Implementation 
The survey will be created and administered through Google Forms for efficient data collection and secure storage. The main survey sections and example questions are outlined below.

@@

**Survey Overview** \
**Title:** 2024 US Presidential Election Poll \
**Purpose:** To collect public opinions and forecast election outcomes. \
**Estimated Time:** Less than 5 minutes \
**Confidentiality:** Responses are anonymous and used solely for research

Consent to Participate
- I confirm that I understand the purpose of the survey, and I agree to participate.

1. What is your age group?
- Under 18
- 18-24
- 25-34
- 35-44
- 45-54
- 55-64
- 65-74
- 75 and older

2. What is your gender identity?
- Male
- Female
- Non-binary
- Prefer not to disclose

3. What is the highest level of education you have completed?
- Less than high school
- High school diploma or GED
- Some college, no degree
- Associate’s degree
- Bachelor’s degree
- Master’s degree
- Doctorate or professional degree (e.g., MD, JD, PhD)

4. Are you currently registered to vote in the United States?
- Yes
- No, but I am eligible and plan to register before the election
- No, and I am not planning to register
- No, I am not eligible to vote in the United States

5. What is your current political affiliation?
- Republican
- Democrat
- Independent 
- Libertarian
- Green Party
- Prefer not to disclose

6. How would you describe your political views?
- Very conservative
- Somewhat conservative
- Moderate
- Somewhat liberal
- Very liberal
- Prefer not to disclose

7. Who do you currently support in the 2024 U.S. presidential election?
- Donald Trump (Republican)
- Kamala Harris (Democrat)
- Undecided
- Other

8. How likely are you to vote in the 2024 presidential election?
- Extremely likely 
- Very likely 
- Moderately likely 
- Somewhat likely 
- Not at all likely

@@

## Conclusion
This survey methodology uses stratified sampling, multi-channel recruitment, and data validation procedures to ensure accurate forecasting of the 2024 US Presidential Election. Through poll-of-polls aggregation, it offers a stable and reliable prediction by mitigating fluctuations in individual polls. The design aims to balance accuracy, inclusivity, and efficiency within a $100K budget, offering meaningful insights into voter behavior and sentiment.
